---
title: "Statistical Concepts"
---

````{r}
#| include: false
random_vars <- readRDS("./Causal_Data_Science_Data/random_vars.rds")
````

## For each variable, compute the following values.
````{r}
expected_value_income <- mean(random_vars$income)
expected_value_age <- mean(random_vars$age)

sd_income <- sd(random_vars$income)
sd_age <- sd(random_vars$age)

var_income <- var(random_vars$income)
var_age <- var(random_vars$age)

cat("Expected Value (Income):", expected_value_income, "\n")
cat("Expected Value (Age):", expected_value_age, "\n\n")

cat("Standard Deviation (Income):", sd_income, "\n")
cat("Standard Deviation (Age):", sd_age, "\n\n")

cat("Variance (Income):", var_income, "\n")
cat("Variance (Age):", var_age, "\n")
````

## Explain, if it makes sense to compare the standard deviations.
No, because the units are different.

## Then, examine the relationship between both variables and compute:
````{r}
covariance <- cov(random_vars)
correlation <- cor(random_vars)

cat("Covariance:", covariance[1,2], "\n")
cat("Correlation:", correlation[1,2], "\n")
````

## What measure is easier to interpret? Please discuss your interpretation.
Correlation is better to interpret, because it is defined between [-1, 1] and therefore unit less. That means, e.g. if the correlation goes against 1, it approaches the maximum. This cannot be seen with covariance.

## Compute the conditional expected value for:
````{r}
expected_value_income_under18 <- mean(random_vars$income[random_vars$age<=18])
expected_value_income_18to65 <- mean(random_vars$income[random_vars$age>18 & random_vars$age<65])
expected_value_income_over65 <- mean(random_vars$income[random_vars$age>=65])

cat("Expected Income under 18:", expected_value_income_under18, "\n")
cat("Expected Income between 18 and 65:", expected_value_income_18to65, "\n")
cat("Expected Income over 65:", expected_value_income_over65, "\n")
````
