---
title: "Directed Acyclic Graphs"
---


## Parking spot DAG
```{r}
#| warnings: false
library(tidyverse)
library(dagitty)
library(ggdag)


schooling_2 <- dagify(
  parking_spots ~ location,
  sales ~ location,
  sales ~ parking_spots,
  coords = list(x = c(parking_spots = 1, location = 2, sales = 3),
                y = c(parking_spots = 1, location = 2, sales = 1))
)

# Plot DAG
ggdag(schooling_2, text = F) +
  geom_dag_point(color = "blue") +
  geom_dag_text(color = NA) +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = name))

```

## Regression models
```{r}
#| warnings: false
df <- readRDS("./Causal_Data_Science_Data/customer_sat.rds")

lm <- lm(satisfaction ~ follow_ups, data = df)
summary(lm)

lm_all <- lm(satisfaction ~ follow_ups + subscription, data = df)
summary(lm_all)
```

## Explanation
In the first model the coefficient for follow ups is -3.3, which means that for every follow up call the satisfaction goes down.
In the second model the coefficient is 2.19, meaning the satisfaction goes up 2.19 points per follow up. 
This makes more sense, as a follow up call is unlikely to decrease customer satisfaction. The reason for this is, that model 2 also takes subscriptions into account.

## Plot data
````{r}
#| warnings: false
#| 
#| # Not conditioning on subscription
data_not_cond <- ggplot(df, aes(x = follow_ups, y = satisfaction)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F)

data_not_cond
````

````{r}
#| warnings: false

# Conditioning on subscription  
data_cond <- ggplot(df, aes(x = follow_ups, y = satisfaction, color = subscription)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F) +
  theme(legend.position = "right")

data_cond
````


