---
title: "Instrumental Variables"
---


## DAG
```{r}
#| warning: false

library(tidyverse)
library(dagitty)
library(ggdag)
library(estimatr)

df <- readRDS("./Causal_Data_Science_Data/rand_enc.rds")

dag <- dagify(
  
  time_spent ~ unobserved,
  time_spent ~ used_ftr,
  used_ftr ~ rand_enc,
  used_ftr ~ unobserved,
  coords = list(x = c(used_ftr = 1, time_spent = 3, rand_enc = 0, unobserved = 2),
                y = c(used_ftr = 1, time_spent = 1, rand_enc = 1, unobserved = 2))
)

# Plot DAG
ggdag(dag, text = F) +
  geom_dag_point(color = "blue") +
  geom_dag_text(color = NA) +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = name))

```


## Naive estimate
```{r}
# Naive estimate
lm_naive <- lm(time_spent ~ used_ftr, data = df)
summary(lm_naive)

```


## Correlations
```{r}
# Display correlations
print(cor(df))
```
Using IV is adequate, because the instrumental variable rand_enc is somewhat correlated to the treatment variable. This means the instrumental relevance is satisfied. It can therefore help to display the effect of the unknown variables. As for the other assumptions, they should be satisfied but we cannot be a 100% certain.

## IV
```{r}
# IV estimate using 2SLS
iv_model <- iv_robust(time_spent ~ used_ftr | rand_enc, data = df)

# Display the IV estimate
summary(iv_model)
```
The treatment effect for the iv model is slightly higher than the biased model. That means there is a downward bias, but it is rather small.